### 2021-02-01 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
method 10

This is where, Ripple Down Rules (RDR) knowledge base, steps in. RDR, by design, provides a safe and traceable data structure for creating, maintaining, and evolving knowledge, in the form of iterpretable rules \cite{compton1992ripple, richards2009two, kim2018rdr}. As \textbf{figRDR} shows, the RDR implementation, which serves as our schema map knowledge base, is very closely related to our schema matching algorithm. Beyond the root node of the RDR, which represents the default condition, at lower depths, syntactic matching characteristics are represented, while semantic matching characteristics, such as the concepts associated with semantic types, follow thereafter. ``AttributeType" elements representing the data types of the attributes as ``string", ``integer", ``double", and ``boolean" are placed in the first case, followed by convertible types, such as the case where the attribute values, in the form of integers are placed in a string (``\textit{1}",``\textit{2}", and so on). The ``Except" clauses then point towards various ``SemanticType", collected from UMLS. Here, the conditional part of the node refers to types such as (``\textit{Sign or Symptom}", ``\textit{Organism Function}", ``\textit{organism Attribute}", and so on), while the conclusion part refers to concepts, such as (``\textit{Fever}", ``\textit{blood pressure}", ``\textit{age}", and so on). In this way, the RDR based knowledge base, provides us with a concrete, memoized, tree data structure, that can be used for schema matching, on the fly.

\subsection*{Schema Map evolution}
\label{schema_map_evol}

>>>>

This is where, Ripple Down Rules (RDR) knowledge base, steps in. RDR, by design, provides a safe and traceable data structure for creating, maintaining, and evolving knowledge, in the form of iterpretable rules \cite{compton1992ripple, richards2009two, kim2018rdr}. As \textbf{figRDR} shows, the RDR implementation, which serves as our schema map knowledge base, is very closely related to our schema matching algorithm. Beyond the root node of the RDR, which represents the default condition, at lower depths, syntactic matching characteristics are represented, while semantic matching characteristics, such as the concepts associated with semantic types, follow thereafter. ``AttributeType" elements representing the data types of the attributes as ``string", ``integer", ``double", and ``boolean" are placed in the first case, followed by convertible types, such as the case where the attribute values, in the form of integers are placed in a string (``\textit{1}",``\textit{2}", and so on). The ``Except" clauses then point towards various ``SemanticType", collected from UMLS. Here, the conditional part of the node refers to types such as (``\textit{Sign or Symptom}", ``\textit{Organism Function}", ``\textit{organism Attribute}", and so on), while the conclusion part refers to concepts, such as (``\textit{Fever}", ``\textit{blood pressure}", ``\textit{age}", and so on). In this way, the RDR based knowledge base, provides us with a concrete, memoized, tree data structure, that can be used for schema matching, on the fly. In moving from root to the leaf nodes of this tree, we gain additional matching characteristics, which are all accumulated in the returned results to provide traceability for the decision makers. Additionally, the RDR creation and subsequently evolution process, is dependent on approval by the expert, in determining which cases can be added to the knowledge base. This combination of automated process for building the schema maps, followed by expert intervention to approve the results, enables a safe and consistent knowledge base.

\subsection*{Schema Map application}
\label{schema_map_evol}
